### 2022-09-26 README.Rmd
drop the .

# nhanesTrends <img src="man/figures/logo.png" align="right" height="139" />

@@

``` r
# install.packages("remotes")
remotes::install_github("jhs-hwg/nhanesShinyBP")
```

@@

library(nhanesShinyBP)
app_run()

>>>>

# cardioStatsUSA <img src="man/figures/logo.png" align="right" height="139" />

@@

``` r
# install.packages("remotes")
remotes::install_github("jhs-hwg/cardioStatsUSA")
```

@@

library(cardioStatsUSA)
app_run()
